\chapter{Limitations and Future Work}

\section{Current Limitations}
\subsection{Dataset and Labeling}
\begin{itemize}[leftmargin=2em]
\item Class imbalance remains visible (for example, tiger vs boar support counts).
\item Background and lighting variation may still be limited compared to production use.
\item Label naming mismatch (hare vs rabbit aliasing) adds integration complexity.
\end{itemize}

\subsection{Model and Inference}
\begin{itemize}[leftmargin=2em]
\item RandomForest operates on per-frame static features and does not model temporal dynamics directly.
\item Confidence thresholds require manual tuning per runtime environment.
\item Similar hand poses can still produce occasional confusion.
\end{itemize}

\subsection{iOS Runtime and UX}
\begin{itemize}[leftmargin=2em]
\item Performance and stability may vary by device generation and camera quality.
\item Effects and tracking quality are sensitive to fast motion blur and partial occlusion.
\item Guidance timing and hold duration messaging should remain synchronized with logic constants.
\end{itemize}

\section{Addressed Since v1}
\begin{itemize}[leftmargin=2em]
\item Leak-free evaluation protocol honoring the Roboflow train/valid/test split (\texttt{\detokenize{train_unified_v2.py}}), with per-class reports and a documented augmentation study.
\item Unified-only CoreML model loading with loud failure instead of silent fallback to incompatible legacy models.
\item Rolling inference-latency instrumentation in \texttt{GestureRecognizer}.
\item Clock injection in \texttt{JutsuManager.processCandidate} and a 14-test SwiftPM suite (\texttt{swift\_tests/}) covering hold-to-commit, flicker rejection, label aliasing, sequence triggers, time limits, and battle-mode counters.
\end{itemize}

\section{Resolved Issues}
\begin{itemize}[leftmargin=2em]
\item \textbf{Kuchiyose unreachable in free mode (fixed via trigger deferral)}: its sequence (boar, horse, monkey, bird) contains wind's (horse, monkey) as a substring, so wind used to fire at the monkey step and clear the sign history. The fix defers a completed short jutsu for a 1.8\,s grace window whenever the sign history is still a live prefix of a longer sequence that contains it: the short jutsu fires when the window expires (player stopped signing) and is discarded when the longer jutsu completes. Standalone short sequences are unaffected. Covered by three unit tests in \texttt{swift\_tests/}.
\end{itemize}

\section{Battle Mode v2}
The battle system was reworked for interactivity:
\begin{itemize}[leftmargin=2em]
\item Enemy projectiles now deal chip damage when they cross the player's zone during the defend phase, making defense time-critical rather than a passive pass/fail check.
\item Defense grading: countering within the first 3\,s of the defend phase scores a \emph{Perfect Block} (+10 chakra).
\item Attack-phase combos: chaining jutsu within a 4\,s window raises a damage multiplier (up to 1.6$\times$) with on-screen combo feedback.
\item Difficulty scaling: enemy barrage rate increases 8\% per round, defend windows shorten, and failed-defense damage grows.
\item Feedback layer: impact-burst rings, enemy hit-flash, screen shake on player damage, distinct victory/defeat overlays, and haptic feedback for sign commits, triggers, blocks, and hits.
\end{itemize}

\section{Recommended Improvements}
\begin{enumerate}[leftmargin=2em]
\item Add temporal modeling (sequence-aware classifier or lightweight recurrent model).
\item Expand training data with multi-user and multi-environment captures.
\item Automate threshold calibration and per-class confidence analysis.
\item Add model versioning and reproducible experiment logging.
\item Build an automated evaluation suite for on-device regression testing.
\item Integrate screenshot and telemetry capture for documentation updates.
\end{enumerate}

\section{Documentation Maintenance Plan}
\begin{itemize}[leftmargin=2em]
\item Update metrics tables after each model retrain.
\item Replace placeholders with latest app screenshots before submission.
\item Keep jutsu-sequence table aligned with \texttt{AppModels.swift} source changes.
\end{itemize}
